### 2013-05-03 paper/tex/conclusion.tex
paper revision extra.

\section{Conclusion}\label{sec:conclusion}
In this document, we describe the design and implementation of CloudCache framework. Through the evaluation, we find that the advantages of CloudCache framework has larger margin for the hard solving problem instances. We also look into the generalness of the framework by designing the solutions for the \emph{k-coloring} problem in the graph. The the solution paradigm fits into the problem very well, which reinforce the advantages of CloudCache framework. Finally, the system performance in CPU and network-in/out evaluation provides us a good fingerprints of the CloudCache framework as a whole.

>>>>

\section{Conclusion}\label{sec:conclusion}
In this document, we describe the design and implementation of CloudCache framework. Through the evaluation, we find that the advantages of CloudCache framework has larger margin to solve harder problem instances. We also look into the generalness of the framework by designing the solutions for the \emph{k-coloring} problem in the graph. The the solution paradigm fits into the problem very well, which reinforces the advantages of CloudCache framework. Finally, the system performance in CPU and network-in/out evaluation provides us a good fingerprints of the CloudCache framework as a whole.
